Constraints on the mass and occupation fraction of dark matter halos hosting Lyman-alpha emitters at $z\sim 3$

### 2013-07-17 paper/ms.tex
paragraph update in the model description

The lower limit for the parameter $M_{\rm min}$ IS set by the
observational constraints on the stellar mass $M_{
\rm star}>2\times 10^{9}$\hMsun \citep{Gawiser07}. Considering a
extreme case where all baryonic mass is in the form of stars an under
the assumption that the baryon to dark matter ratio cannot be larger
than the cosmological value $\Omega_{\rm b}/Omega_{\rm dm}\sim 0.2$,
the minimum value for the dark matter halo that we should consider is
precisely $\sim 10^{10}$\hMsun. In turn, this limit help us impose the
minimum value of $f_{\rm occ}=0.1$. Lower values for the occupation
fraction would produce a halo number density well below the observational
constraints.

>>>>

The lower limit for the parameter $M_{\rm min}$ is set by the minium
occupation fraction we are able to consider. At $M_{\rm
  min}=10^{10}$\hMsun the halo number density is already $\sim 10$
times higher than the observational constraints for LAEs. This means
that models in that mass range and an occupation fraction $f_{\rm
  occ}$ have the possibility to be compatible with observations. Lower
values for $M_{\rm min}$ require $f_{\rm occ}<0.1$, which are not
considered in this \documentname.
